---
title: "Mini_Project_3"
author: "Stephanie and Felicia"
date: "April 15, 2018"
output: 
  html_document:
    code_folding: hide
---

```{r message = FALSE, warning=FALSE}
#This code chunck loads all the packages we used for this project:

library(tidyverse)
library(macleish)
library(sf)
library(leaflet)
```

We decided to explore the MacLeish spatial data and propose two new campsite locations we feel would be ideal given some constraints.  We used GitHub to collaborate with each other during this project. [^1] Enjoy our blog!


#**Camping - It's IN-TENTS**

##*Leave No Trace Campsite Initiative*


###Problem Statement

Smithies study hard and need a safe nurturing environment to destress and learn wilderness skills. The existing campsites are not sufficient to sustain the growing population at campus. Smith needs two new campsites to facilitate enhanced educational outreach and an experience with nature for current students. Smith students deserve a place where they can disengage from technology and engage with nature. We utilized the below criteria to propose two additional campsites.

- Approximately half a mile walk from parking area
- Within 200 feet of stream or other water source (excluding wetlands)
- In a forest unlike other campsites
- Relatively flat
- At least 500 feet from research areas and challenge course

###Approach

In order to decide where the ideal campsite locations would be, we decided to use the layers in the Macleish package in R to explore the Macleish Field Station.  Initially, we created many different maps with all the criteria listed above, but eventually decided that an interactive leaflet map would be ideal.  Being able to enable and disable layers, makes it easy to see where good campsite locations are. Having each individual layer as a possible box to turn on and off was not very helpful, so we decided to create eight groups. The gorups we crated were, boundaries, existing camping, features to be near, features to avoid, forests, slope, possible camping and proposed camping.  


###Interactive Leaflet Map

```{r message = FALSE, warning=FALSE}

#Added stream buffers
proj4_aea <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=37.5 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"

stream_buffer <- macleish_layers[["streams"]] %>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 61) %>%
  st_transform(4326)

#Created the color palette for the forests
forest_pal <- colorFactor("Greens", macleish_layers[["forests"]]$Sheet1__Na)
```

```{r message = FALSE, warning=FALSE}
    # Added a point for the parking area to use as a central point in our map
  parking <- data.frame(lat = 42.448013, lon = -72.680663)
  map <- leaflet() %>%
    
    # Break map information into logical groups that can be turned on and off
    # Base groups
  addTiles(group = "OpenStreetMap") %>%
  addProviderTiles("Esri.WorldImagery", group = "Satellite") %>%
  
    # Boundaries
  addPolygons(data = macleish_layers[["boundary"]], weight = 1, group = "Boundaries") %>%
  
    # Existing Camping Features
  addMarkers(lng = -72.678154, lat = 42.455000, 
             popup = "Group Campsite", group = "Existing Camping") %>%
  addMarkers(lng = -72.679581, lat = 42.458549, 
             popup = "Remote Campsite", group = "Existing Camping") %>%
  addMarkers(lng = -72.680663, lat = 42.448013, 
             popup = "Parking", group = "Existing Camping") %>%
  
    # Stay Close to Trails, Streams (in 61 m buffer) and Parking (805 m)
  addPolylines(data = macleish_layers[["trails"]], 
               weight = 1, color = "brown",
               popup = ~ name, group = "Features to be Near") %>%
  addPolylines(data = macleish_layers[["streams"]], 
               weight = 2, group = "Features to be Near") %>%
  addPolygons(data = stream_buffer, weight = 1, group = "Features to be Near") %>%
  addCircles(lng = -72.680663, lat = 42.448013, 
             weight = 2, opacity = .5, radius = 805, group = "Features to be Near") %>%
  
    # Avoid Wetlands, Research Plots (152 m), and Challenge Course (152 m)
  addPolygons(data = macleish_layers[["wetlands"]], 
              weight = 1, group = "Features to Avoid") %>%
  addPolygons(data = macleish_layers[["research"]], 
               weight = 1, color = "orange", group = "Features to Avoid") %>%
  addCircles(lng = -72.6835, lat = 42.4542, 
             weight = 1, radius = 152, color = "orange", 
             label = "research buffer", group = "Features to Avoid") %>%
  addCircles(data = macleish_layers[["challenge_courses"]], 
                   radius = 1, color = "orange", group = "Features to Avoid") %>%
  
    # Consider Forest Type and Slope
  addPolygons(data = macleish_layers[["forests"]], 
              color = ~forest_pal(Sheet1__Na), weight = 0.1, 
              fillOpacity = 0.2,
              popup = ~ Sheet1__Na, group = "Forests") %>%
  addPolylines(data = macleish_layers[["contours_3m"]], color = "gray", 
               weight = 1, group = "Slope") %>%
    
    # Possible Camping Sites
  addCircleMarkers(lng = -72.6858, lat = 42.4546, color = 'green', group = "Possible Camping") %>%
  addCircleMarkers(lng = -72.6762, lat = 42.4535, color = 'green', group = "Possible Camping") %>%
  addCircleMarkers(lng = -72.6790, lat = 42.4444, color = 'green', group = "Possible Camping") %>%
  addCircleMarkers(lng = -72.6752, lat = 42.4477, color = 'green', group = "Possible Camping") %>%
  addCircleMarkers(lng = -72.6737, lat = 42.4493, color = 'green', group = "Possible Camping") %>%
  
    # Proposed Camping Sites
  addMarkers(lng = -72.6858, lat = 42.4546, 
             popup = "Proposed Campsite 1", group = "Proposed Sites") %>%
  addMarkers(lng = -72.6737, lat = 42.4493, 
             popup = "Proposed Campsite 2", group = "Proposed Sites") %>%
  
    # Layers control
  addLayersControl(
    baseGroups = c("OpenStreetMap", "Satellite"),
    overlayGroups = c("Boundaries", "Existing Camping", "Features to be Near", 
                      "Features to Avoid", "Forests", "Slope", "Possible Camping", "Proposed Sites"),
                      options = layersControlOptions(collapsed = FALSE)
  ) %>%
  
    # Set opening view center on the parking area
    setView(lat = parking$lat, lng = parking$lon, zoom = 14)
map
```



###Campsites Chosen and Proposed Solution

For our proposed camping sites, we chose an area on the upper left corner of the Macleish Property in the Red Oak Forest. Using the interactive leaflet map, you will see that it is within 200 feet of a stream, withing a 1/2 mile radisu from the parking area, in a different forest from the other campsites, relatively flat and at least 500 feet away from the research areas and challenge course.  Our other proposed camping area is on the right side of the property closr to the bottom part of Macleish.  This site is in the Hemlock-Northern Hardwoods Forest and all the requirements and restrictions apply.  There two camping sites would be easy to create since they are not in abandoned pasture and will be pretty for the people to spend time in.

We feel that Smith College should build two basic campgrounds providing sleeping space for 12 with fire rings for open cooking. The estimated time is approximately two to four weeks per site. The cost to outfit each site will range between $4,000 to $6,000 per site. Smith College should have all the required tools for groundwork. Fire Rings for the cooking facilities are available at any home improvement warehouse. The initial outfitting for student supplies, such as tents, sleeping bags, and other camping gear can be acquired at a rate of approximately $350 per student initial investment. 


###Further Recommendation

We would also suggest conducting an Environmental Impact Study on the feasibility and impact of adding a bathroom facility. The cost for a bathroom facility would be approximately $25,000. The environmental impact study could advise further specifics such as the treatment and removal of grey water and waste water. This would fall outside our Leave No Trace Campsite initiative but would greatly enhance camper enjoyment. The ability to have bathrooms and shower availability would increase the camper count.


###Anticipated Roadblocks

We feel adhering to the core Leave No Trace principles adopted by the MacLeish Advisory should encourage board approval for our planned camp site. Environmental impact of site preparation will be minimal.  All efforts will be made to avoid disruption.  No excavation (other than clearing an area for the cooking area) is anticipated.  Visitors will be expected to adhere to the Leave No Trace principles.  Therefore, no latrine or pit facilities will be constructed.   However, there are always environmental impacts of human activity (trampled vegetation, human waste in ‘catholes’, biodegradable soap used to wash up, etc.) and these should not be ignored. A major possible roadblock is the funding.  Smith and the Macleish Field Station shoudl come up with the funding for these campsites.

###Data Utilized

The data that we utilized for our analysis was the MassGIS (Bureau of Geographic Information) for elevation/topographic data and stream locations. The general MacLeish Field Station including boundaries was provided to us in the "MacLeish" Package. For outside reference we utilized the ***KOA** 2017 Annual North American Camping Report* as well as *Start Up Jungle*.


####References

http://www.koapressroom.com/press/2017-north-american-camping-report-released/

https://lnt.org/learn/7-principles

https://www.smith.edu/ceeds/macleish.php

https://www.smith.edu/ceeds/form_camping.php

https://www.tripsavvy.com/setting-up-a-campsite-498429



[^1]: [This is the link to the github repository](https://github.com/sfoukaris/Mini_Project_3.git)